Computing Entropies With Nested Sampling

### 2017-06-28 paper/ms.tex
Results

The results for the uneven observing schedule, again in terms of log
probabilities, are:
\begin{align}
\depth_{\tau}      &= 6.216  \pm 0.025 \\
\depth_{\d}        &= 479.47 \pm 0.31  \\
\depth_{\tau, \d}  &= 480.27 \pm 0.32  \\
I(\tau; \d)        &= 4.69 \pm 0.32
\end{align}

The difference in mutual informations between the two observation
schedules, assuming a uniform prior on this difference,
is just $0.98 \pm 0.44$ nats, suggesting (extremely weakly)
a slight advantage to the
even observing schedule, in terms of the data's relevance to inference
of the log-period of the signal. The situation may be different if we
had allowed for shorter periods to be possible, as irregular observing
schedules are known to reduce aliasing and ambiguity in the inferred period.
When inferring the period of an oscillating signal, multimodal posterior
distributions for the period are common \citep{gregoryTrimodal, exoplanet}.
The multimodality of the posterior here raises an interesting issue. Is
the question we really want answered ``what is the value of $T$
{\bf precisely}?'', to which the mutual information relates?
Most practicing scientists would not feel particularly informed to learn
that the vast majority of possibilities had been ruled out, if the
posterior still consisted of several widely separated modes!
Perhaps, in some applications, a more appropriate question is
``what is the value of $T$ to within $\pm$ 10\%'', or something along these
lines.

>>>>

The results for the uneven observing schedule were
\begin{align}
\depth       &=  5.422 \pm 0.038 \\
H(\tau | \d) &= -5.398 \pm 0.038 \\
I(\tau; \d   &=  5.398 \pm 0.038 \textnormal{ nats}.
\end{align}

The difference in mutual informations between the two observation
schedules is trivial.
The situation may be different if we
had allowed for shorter periods to be possible, as irregular observing
schedules are known to reduce aliasing and ambiguity in the inferred period.
When inferring the period of an oscillating signal, multimodal posterior
distributions for the period are common \citep{gregoryTrimodal, exoplanet}.
The multimodality of the posterior here raises an interesting issue. Is
the question we really want answered ``what is the value of $T$
{\bf precisely}?'', to which the mutual information relates?
Most practicing scientists would not feel particularly informed to learn
that the vast majority of possibilities had been ruled out, if the
posterior still consisted of several widely separated modes!
Perhaps, in some applications, a more appropriate question is
``what is the value of $T$ to within $\pm$ 10\%'', or something along these
lines.
